---
title: "func-descr.template"
output: html_document
---

#### [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) Function {#func.log_func_tmpl}
\


::: { #func.log_func_tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}

```
:::

::: { #func.log_func_tmpl.args .sidebar }
##### Arguments
\

::: { #func.log_func_tmpl.args.file_name .sidebar }
  - **file_name:** A name used as a base to generate a unique log file name; 

:::
:::

::: { #func.log_func_tmpl.details .sidebar }
##### Details
\


:::

::: { #func.log_func_tmpl.value .sidebar }
##### Value
\


:::

::: { #func.log_func_tmpl.code .sidebar }
##### Source Code
\

The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is shown below:
```{r eval=FALSE}

```

::: {.noteblock data-latex=""}
The source code of the [log_func_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) function is defined in the [logging-functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/logging-functions.R#Lx) script on _GitHub_.
:::
:::













#### [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.cmmn_helper_func.tmpl}
\

::: { #func.cmmn_helper_func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
cmmn_helper_func.tmpl()

```
:::

::: { #func.cmmn_helper_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.cmmn_helper_func.tmpl.args. .sidebar }
  - **:** ; 

:::
::: { #func.cmmn_helper_func.tmpl.args. .sidebar }
  - **:** ; 

:::
:::

::: { #func.cmmn_helper_func.tmpl.details .sidebar }
##### Details
\



:::

::: { #func.cmmn_helper_func.tmpl.value .sidebar }
##### Value
\

:::

::: { #func.cmmn_helper_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [cmmn_helper_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L0) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
:::
:::

#### [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) Function {#func.RMSEs.tibble_tmpl}
\

Modifies the original _RMSEs Result Tibble_ passed in the [RMSEs](#func.RMSEs.tibble_tmpl.args.RMSEs) argument.

::: { #func.RMSEs.tibble_tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
```
:::

::: { #func.RMSEs.tibble_tmpl.args .sidebar }
##### Arguments
\

::: { #func.RMSEs.tibble_tmpl.args.RMSEs .sidebar }
  - ***RMSEs:*** Original _RMSEs Result Tibble_ (of type *data frame*) to modify;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::

::: { #func.RMSEs.tibble_tmpl.args. .sidebar }
  - ***:*** ;

:::
:::

::: { #func.RMSEs.tibble_tmpl.details .sidebar }
##### Details
\

This function is a wrapper for the [tibble::]() function, which is called internally to modify a data frame representing the original _RMSEs Result Tibble_, which stores the _RMSE_ values for the models used in the project to predict movie ratings.

For more information about the _RMSEs Result Tibble_, see the [Details](#func.CreateRMSEs_ResultTibble.details) section of the [CreateRMSEs_ResultTibble](#func.CreateRMSEs_ResultTibble) function description above.
:::

::: { #func.RMSEs.tibble_tmpl.value .sidebar }
##### Value
\

The modified tibble returned by the internally called [tibble::()]().

:::


::: { #func.RMSEs.tibble_tmpl.code .sidebar }
##### Source Code
\

The source code of the [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```
:::

::: {.noteblock data-latex=""}
The source code of the [RMSEs.tibble_tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) function is also available in the [RMSEs Result Tibble](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L15) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#LX) script on _GitHub_.
:::

\newpage


## Data Helper Functions
\
#### [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.dat_func.tmpl}
\

::: { #func.dat_func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
dat_func.tmpl()

```
:::

::: { #func.dat_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.dat_func.tmpl.args.data .sidebar }
  - **data:** ; 

:::
::: { #func.dat_func.tmpl.args. .sidebar }
  - **:** ; 

:::
:::

::: { #func.dat_func.tmpl.details .sidebar }
##### Details
\



:::

::: { #func.dat_func.tmpl.value .sidebar }
##### Value
\

:::

::: { #func.dat_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [dat_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
:::
:::







### Data processing function
\

#### [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) Function {#func.datproc_func.tmpl}
\

::: { #func.datproc_func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
```
:::

::: { #func.datproc_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.datproc_func.tmpl.args.data .sidebar }
  - **data:** ; 

:::
::: { #func.datproc_func.tmpl.args.seed .sidebar }
  - **seed:** ; 

:::
:::

::: { #func.datproc_func.tmpl.details .sidebar }
##### Details
\



:::

::: { #func.datproc_func.tmpl.value .sidebar }
##### Value
\

:::

::: { #func.datproc_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [datproc_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) function is also available in the [Data processing functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L3) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#LX) script on _GitHub_.
:::
:::











## Model Helper Functions
### Overal Mean Rating (OMR) Model Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R) script on _GitHub_.
:::

#### [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) Function {#func.OMR_model_func.tmpl}
\

::: { #func.OMR_model_func.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
OMR_model_func.tmpl()

```
:::

::: { #func.OMR_model_func.tmpl.args .sidebar }
##### Arguments
\

::: { #func.OMR_model_func.tmpl.args. .sidebar }
  - **x:** ; 

:::
:::

::: { #func.OMR_model_func.tmpl.details .sidebar }
##### Details
\



:::

::: { #func.OMR_model_func.tmpl.value .sidebar }
##### Value
\

:::

::: { #func.OMR_model_func.tmpl.code .sidebar }
##### Source Code
\

The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [OMR_model_func.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) function is defined in the [OMR-model.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/OMR-model.functions.R#LX) script on _GitHub_.
:::
:::

\newpage

### UME Model Utility Functions
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) script on _GitHub_.
:::

#### [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) Function {#func.ume_helper.tmpl}
\

::: { #func.ume_helper.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
ume_helper.tmpl()

```
:::

::: { #func.ume_helper.tmpl.args .sidebar }
##### Arguments
\

::: { #func.ume_helper.tmpl.args. .sidebar }
  - **:** ; 

:::
::: { #func.ume_helper.tmpl.args. .sidebar }
  - **:** ; 

:::
:::

::: { #func.ume_helper.tmpl.details .sidebar }
##### Details
\



:::

::: { #func.ume_helper.tmpl.value .sidebar }
##### Value
\

:::

::: { #func.ume_helper.tmpl.code .sidebar }
##### Source Code
\

The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [ume_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
:::
:::

\newpage

### UME Model Regularization
\

::: {.noteblock data-latex=""}
The complete source code of the functions described in this section is available in the  [UME Model Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) script on _GitHub_.
:::

#### [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) Function {#func.ume_rglr_helper.tmpl}
\

::: { #func.ume_rglr_helper.tmpl.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
ume_rglr_helper.tmpl()

```
:::

::: { #func.ume_rglr_helper.tmpl.args .sidebar }
##### Arguments
\

::: { #func.ume_rglr_helper.tmpl.args. .sidebar }
  - **:** ; 

:::
::: { #func.ume_rglr_helper.tmpl.args. .sidebar }
  - **:** ; 

:::
:::

::: { #func.ume_rglr_helper.tmpl.details .sidebar }
##### Details
\



:::

::: { #func.ume_rglr_helper.tmpl.value .sidebar }
##### Value
\

:::

::: { #func.ume_rglr_helper.tmpl.code .sidebar }
##### Source Code
\

The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [ume_rglr_helper.tmpl](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [UME Model Utility Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L90) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) script on _GitHub_.
:::
:::

\newpage


## General Func Tempates -------------------------------------------------------

#### [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) Function {#func.@@func}
\

::: { #func.@@func.usage .sidebar }
##### Usage
\

```{r eval=FALSE}
@@func()

```
:::

::: { #func.@@func.args .sidebar }
##### Arguments
\

::: { #func.@@func.args. .sidebar }
  - **:** ; 

:::
::: { #func.@@func.args. .sidebar }
  - **:** ; 

:::
:::

::: { #func.@@func.details .sidebar }
##### Details
\



:::

::: { #func.@@func.value .sidebar }
##### Value
\

:::

::: { #func.@@func.code .sidebar }
##### Source Code
\

The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) function is shown below:
```{r eval=FALSE}
```

::: {.noteblock data-latex=""}
The source code of the [@@func](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#LX) function is also available in the [section](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L) section of the [@@script.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/@@script.R#LX) script on _GitHub_.
:::
:::

\newpage
