---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: [references.bib]
#link-citations: true
output:
  html_document: 
    fig_caption: true
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=TRUE}
library(RefManageR)
bib <- ReadBib(system.file("Bib", "references.bib", 
                           package = "RefManageR"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction / Overview / Executive Summary

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the^[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)] requirements, we will evaluate the RMSE score^[Rafael A. Irizarry: Introduction to Data Science, Part II, Section 23.2: Loss function]:  

Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563^[R: A Language and Environment for Statistical Computing, Section 33.6.1 Matrix Factorization, @R-base]). 



```{r cars}
summary(cars)
```

## Methods / Analysis

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Conclusion

Hello Conclusion!

This is a great conclusion, isn't is?!!

## Refs

[Rafael A. Irizarry. Introduction to Data Science, Part II](https://rafalab.dfci.harvard.edu/dsbook-part-2/)

1.23.2 [Section 23.2: Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function)
	
[Töscher, A., Jahrer, M., & Bell, R. M. (2009). The BigChaos Solution to the Netflix Grand Prize](https://www.asc.ohio-state.edu/statistics/statgen/joul_aut2009/BigChaos.pdf)

