## User+Movie Effect (UME) Model
\

In [23.5 Movie effects](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#movie-effects) section of the *Course Textbook* the author draws our attention to the fact that some movies are generally rated higher than others. He also explains that a linear model with a _treatment effect_ $\beta_j$ for each movie can be used in this case, which can be interpreted as movie effect or the difference between the average ranking for movie $j$ and the overall average $\mu$: 

$$
Y_{i,j} = \mu + \alpha_i + \beta_j +\varepsilon_{i,j}
$$
The author then shows how to use an approximation by first computing the least square estimate $\hat{\mu}$ and $\hat{\alpha}_i$, and then estimating $\hat{\beta}_j$ as the average of the residuals $y_{i,j} - \hat{\mu} - \hat{\alpha}_i$:

```{r eval=FALSE}
b <- colMeans(y - mu - a, na.rm = TRUE)
```

Inspired by this idea, a few support functions were developed by the author of this report, which we will use for our further analysis.

\newpage

### UME Model: Support Functions
\

::: {.noteblock data-latex=""}
The full source code of the functions described in this section is available in the [User+Movie Effect Model Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L1) section of the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script on _GitHub_.
:::
 
#### [train_user_movie_effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L2) Function {#func.train_user_movie_effect}
\

We use this function to build and train our model using the `train_set` dataset:
```{r eval=FALSE}
train_user_movie_effect <- function(train_set, lambda = 0){
  if (is.na(lambda)) {
    stop("Function: train_user_movie_effect
`lambda` is `NA`")
  }

  UM.effect <- train_set |>
    left_join(edx.user_effect, by = "userId") |>
    mutate(resid = rating - (mu + a)) |> 
    group_by(movieId) |>
    summarise(b = mean_reg(resid, lambda), n = n())
  
  stopifnot(!is.na(mean(UM.effect$b)))
  UM.effect
}
```

::: {.noteblock data-latex=""}
The function described above accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We also use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call, which we will also need later for the *Regularization* techniques (for details, see the  [mean_reg](#func.mean_reg) function description in the Section [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of the [Appendix] to this report).
We will explain that later in the [User+Movie Effect Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. In this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

\newpage

#### `train_user_movie_effect.cv` Function {#func.train_user_movie_effect.cv}
\

We use the [train_user_movie_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L17) function to build and train our model using the `5-Fold Cross Validation` method. Below, we provide the most important part of the code of that function:
```{r eval=FALSE}
train_user_movie_effect.cv <- function(lambda = 0){
# ...
  start <- put_start_date()
  user_movie_effects_ls <- lapply(edx_CV, function(cv_fold_dat){
    cv_fold_dat$train_set |> train_user_movie_effect(lambda)
  })
  put_end_date(start)
  put_log("Function: train_user_movie_effect.cv:
User+Movie Effect list have been computed")
  
  user_movie_effects_united <- union_cv_results(user_movie_effects_ls)

  user_movie_effect <- user_movie_effects_united |>
    group_by(movieId) |>
    summarise(b = mean(b), n = mean(n))
  # ...
  user_movie_effect
}

```

::: {.noteblock data-latex=""}
Here we use the function call [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432), which is defined in the script [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R), to aggregate the _5-Fold Cross Validation_ method results (for details, see the [union_cv_results](#func.union_cv_results) function description in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report).
:::

#### `calc_user_movie_effect_MSE` Function
\

The code of the function [calc_user_movie_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L55) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Mean Squared Error (MSE)` of the `UME Model` for the given `Test Set` is provided below:
```{r eval=FALSE}
calc_user_movie_effect_MSE <- function(test_set, um_effect){
  mse.result <- test_set |>
    left_join(edx.user_effect, by = "userId") |>
    left_join(um_effect, by = "movieId") |>
    mutate(resid = rating - clamp(mu + a + b)) |> 
    pull(resid) |> mse()
  
  stopifnot(!is.na(mse.result))
  mse.result
}
```

#### `calc_user_movie_effect_MSE.cv` Function
\

The code of the function [calc_user_movie_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L72) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` MSE result of the `UME Model` is provided below:
```{r eval=FALSE}
calc_user_movie_effect_MSE.cv <- function(um_effect){
  put_log("Function: user_movie_effects_MSE.cv:
Computing the RMSE taking into account User+Movie Effects...")
  start <- put_start_date()
  user_movie_effects_MSEs <- sapply(edx_CV, function(cv_fold_dat){
    cv_fold_dat$validation_set |> calc_user_movie_effect_MSE(um_effect)
  })
  put_end_date(start)
  
  put_log1("Function: user_movie_effects_MSE.cv:
MSE values have been plotted for the %1-Fold Cross Validation samples.", 
           CVFolds_N)
  
  mean(user_movie_effects_MSEs)
}

```


#### `calc_user_movie_effect_RMSE` Function
\


The code of the function [calc_user_movie_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L51) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `Root Mean Squared Error (RMSE)` of the `UME Model` for the given `Test Set` is provided below:

```{r eval=FALSE}
calc_user_movie_effect_RMSE <- function(test_set, um_effect){
  mse <- test_set |> calc_user_movie_effect_MSE(um_effect)
  sqrt(mse)
}
```

#### `calc_user_movie_effect_RMSE.cv` Function
\

The code of the function [calc_user_movie_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L65) defined in the [UM-effect.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R) script to calculate the `5-Fold Cross Validation` RMSE result of the `UME Model` is provided below:

```{r eval=FALSE}
calc_user_movie_effect_RMSE.cv <- function(um_effect){
  user_movie_effects_MSE <- calc_user_movie_effect_MSE.cv(um_effect)
  um_effect_RMSE <- sqrt(user_movie_effects_MSE)
  put_log2("Function: user_movie_effects_RMSE.cv:
%1-Fold Cross Validation ultimate RMSE: %2", CVFolds_N, um_effect_RMSE)
  um_effect_RMSE
}

```

\newpage

### Model Building
\

::: {.noteblock data-latex=""}
The full source code of builing and training the current model is available in the [Model building: User+Movie Effect](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L721) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script on _GitHub_.
:::

Below, we provide the most significant part of the code for training our model using the `5-Fold Cross Validation` method:
```{r eval=FALSE}
  cv.UM_effect <- train_user_movie_effect.cv()
```
```{r}
str(cv.UM_effect)

par(cex = 0.7)
hist(cv.UM_effect$b, 30, xlab = TeX(r'[$\hat{beta}_{j}$)]'),
     main = TeX(r'[Histogram of $\hat{beta}_{j}$]'))
```


We can now construct predictors and see how much the `RMSE` improves[@IDS2_23-5]:
```{r eval=FALSE}
cv.UM_effect.RMSE <- calc_user_movie_effect_RMSE.cv(cv.UM_effect)

RMSEs.ResultTibble.UME <- RMSEs.ResultTibble.UE |> 
  RMSEs.AddRow("User+Movie Effect Model", cv.UM_effect.RMSE)

```
```{r}
RMSE_kable(RMSEs.ResultTibble.UME)
```

### User+Movie Effect Model Regularization
\

#### Utilizing Penalized least squares
\

[Section _23.6 Penalized least squares_ of the *Course Textbook*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#penalized-least-squares) explains why and how we should use _Penalized least squares_ to improve our predictions. The author also explains that the general idea of penalized regression is to control the total variability of the movie effects: $\sum_{j=1}^n \beta_j^2$. Specifically, instead of minimizing the least squares equation, we minimize an equation that adds a penalty:

$$ 
\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j \right)^2 + \lambda \sum_{j} \beta_j^2
$$
The first term is just the sum of squares and the second is a penalty that gets larger when many $\beta_i$s are large. Using calculus, we can actually show that the values of $\beta_i$ that minimize this equation are:

$$
\hat{\beta}_j(\lambda) = \frac{1}{\lambda + n_j} \sum_{i=1}^{n_i} \left(Y_{i,j} - \mu - \alpha_i\right)
$$

where $n_j$ is the number of ratings made for movie $j$. 

This approach will have our desired effect: when our sample size $n_j$ is very large, we obtain a stable estimate and the penalty $\lambda$ is effectively ignored since $n_j+\lambda \approx n_j$. Yet when the $n_j$ is small, then the estimate $\hat{\beta}_i(\lambda)$ is shrunken towards 0. The larger the $\lambda$, the more we shrink[@IDS2_23-6].

We will implement the _Regularization_ method on our  models (starting from the current model) in two steps:

  1. **Preconfiguration:** Preliminary determination of the optimal range of $\lambda$ values for the `5-Fold Cross Validation` samples;
  
  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.


\newpage

#### UME Model Regularization: Support Functions
\

::: {.noteblock data-latex=""}
The [regularize.test_lambda.UM_effect.cv]() function described below are defined in the [Regularization]() section of the [UM-effect.functions.R]() script.
:::

##### [regularize.test_lambda.UM_effect.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UM-effect.functions.R#L96) Function {#func.regularize.test_lambda.UM_effect.cv}
\

This function calculates _RMSE_ of the _UME Model_ using _5-Fold Cross Validation_ method for the given $\lambda$ parameter value:
```{r, eval=FALSE}
regularize.test_lambda.UM_effect.cv <- function(lambda){
  if (is.na(lambda)) {
    stop("Function: regularize.test_lambda.UM_effect.cv
`lambda` is `NA`")
  }
  um_effect <- train_user_movie_effect.cv(lambda)
  calc_user_movie_effect_RMSE.cv(um_effect)
}
```

::: {.noteblock data-latex=""}
Note that we reuse the function [train_user_movie_effect.cv](#func.train_user_movie_effect.cv) calling it from the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv), but now with the $\lambda$ parameter different from the default ('lambda = 0') value.
:::

\newpage

#### User+Movie Effect Model Tuning: Preconfiguratioin
\

Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:

We are going to use the [tune.model_param](#func.tune.model_param) function described in [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) the section of the [Appendix] to this report, passing the [regularize.test_lambda.UM_effect.cv](#func.regularize.test_lambda.UM_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.params.fn_tune.test.param_value) parameter:

```{r, eval=FALSE}
lambdas <- seq(0, 1, 0.1)

cv.UME.preset.result <- 
  tune.model_param(lambdas, regularize.test_lambda.UM_effect.cv)

put_log1("Preliminary regularization set-up of `lambda`s range for the UME Model has been completed
for the %1-Fold Cross Validation samples.",
CVFolds_N)

```
```{r}
str(cv.UME.preset.result)
```

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section can be found in the [Process Preliminary setting-up of lambda range for UM Effect regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L814) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R) script.
:::

Now, let's visualize the results of the $\lambda$ range preconfiguration:
``` {r}
cv.UME.preset.result$tuned.result |>
  data.plot(title = TeX(r'[Preliminary set-up of $\lambda$ for Regularazation of the User+Movie Effect Model.]'),
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = TeX(r'[$\lambda$]'), 
              ylabel = "RMSE")
```

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of the [Appendix] to this report, which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script.
:::



\newpage

#### User+Movie Effect Model: Fine-Tuning

\newpage
