## User+Movie+Genre+Year+Day Effect (UMGYDE) Model
\

### Mathematical Description of the UMGYDE Model
\

If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYDE Model_, for the current model, takes the form:

\begin{equation}
Y_{i,j} = \mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}) + s(d_{i,j}) + \varepsilon_{i,j}
(\#eq:UMGYDE-model)
\end{equation}

with $s$ a _smoothed day_ function of $d_{i,j}$

Therefore, the formula \@ref(eq:year-effect) for calculation the prediction of a _year effect_ as a residual, for a _smoothed day effect_ 
$$
\hat{s}(d_{i,j}) = s(d_{i,j}) + \varepsilon_{i,j}
$$

takes the following form:

\begin{equation}
\hat{s}(d_{i,j}) = Y_{i,j} - (\mu + \alpha_i + \beta_j + g_{i,j} + \gamma(v_{i,j}))
(\#eq:smoothed-day-effect)
\end{equation}

\newpage

### UMGYDE Model Building With Default Parameters
\

::: {.noteblock data-latex=""}
The complete source code of building and training the current model is available in the [UMGYDEM Training with default parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1477) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1477) script on _GitHub_.
:::

We are going to use the helper function ([train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A: Support Functions]) specifically designed to train the *UMGYDE Model*, which under the hood calls the [stats::loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) `R` function, passing its `degree` and `span` parameters values taken from the caller's [degree](#func.train_UMGY_SmoothedDay_effect.cv.args.degree) and [span](#func.train_UMGY_SmoothedDay_effect.cv.args.span) arguments, respectively.

We will start by calling the [train_UMGY_SmoothedDay_effect.cv](#func.train_UMGY_SmoothedDay_effect.cv) with default parameters, which means that the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function will be implicitly called with `degree = 1` and `span = 0.75` arguments - the default values for the auxiliary function [loess_de](#func.loess_de) (described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a)) included in the call chain that actually, calls the [loess](https://www.rdocumentation.org/packages/stats/versions/3.6.2/topics/loess) function.

Below is the [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1495) that trains our model with the default `degree` and `span` parameter values using *K-Fold Cross Validation*, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$):
```{r, eval=FALSE}
  cv.UMGYDE.default_params <- train_UMGY_SmoothedDay_effect.cv()
```
```{r}
str(cv.UMGYDE.default_params)
```

\newpage

Below is the visual representation of the UMGYD Effect data we have just computed:

```{r}
cv.UMGYDE.default_params |>
  ggplot(aes(x = days)) +
  geom_point(aes(y = de), size = 3, alpha = .5, color = "grey") + 
  geom_line(aes(y = de_smoothed), color = "red")
```

Let's calculate the _RMSE_ of the current model using the [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) helper function described in section *Models Training: Support Functions /* [UMGYDE Model: Utility Functions] section of [Appendix A](#appndx_a):

```{r, eval=FALSE}
cv.UMGYDE.default_params.RMSE <- cv.UMGYDE.default_params |>
  calc_UMGY_SmoothedDay_effect.RMSE.cv()

RMSEs.ResultTibble.UMGYDE <- RMSEs.ResultTibble.rglr.UMGYE |> 
  RMSEs.AddRow("UMGYDE (Default) Model", 
               cv.UMGYDE.default_params.RMSE,
               comment = "User+Movie+Genre+Year+Day Effect (UMGYDE) Model 
computed using `stats::loess` function with `degree=1` & `span=0.75` parameter values.")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYDE)
```

::: {.noteblock data-latex=""}
In the code snippet above we also use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in section *Common Helper Functions /* [Result RMSEs Tibble Functions] of [Appendix A](#appndx_a).
:::

Unfortunately, with the default parameters, we obtained an even worse result than before.
Let's tune the current model by adjusting the `degree` and `span` parameters and see what we get.

::: {.noteblock data-latex=""}
Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three steps - one for each possible value of the `degree`.
:::

\newpage

### UMGYDE Model Tuning by `degree` and `span` Parameters
\

#### UMGYDE Model Tuning: Step 1 (`degree = 0`)
\

##### Pre-configuration: `span` Determining the optimal range of the *span* parameter
\

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1558) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1558) script on _GitHub_.
:::

Below is the [lines of code]() that determines the optimal range of `span` for the further model tuning when `degree = 0`:
```{r, eval=FALSE}
  spans <- seq(0.0005, 1, 0.001)
  lss.UMGYDE.preset.degree0.result <- 
    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
```
```{r}
str(lss.UMGYDE.preset.degree0.result)
```

::: {.noteblock data-latex=""}
In the code snippet above, we use the following functions described in [Appendix A: Support Functions]: 
  
  - [tune.model_param](#func.tune.model_param) and [RMSE_kable](#func.RMSE_kable) (described in the *Common Helper Functions /* [Regularization Functions](#appndx_a.CHF.regularization) section) to update and print the table above.

  - [train_UMGY_SmoothedDay_effect.RMSE.cv.degree0](#func.train_UMGY_SmoothedDay_effect.RMSE.cv.degree0) (described in the *Models Training: Support Functions /* [UMGYDE Model: Tuning `loess` Params] section) to calculate the *RMSE* for the *UMGE Model*;
:::

Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
```{r}
plt.title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 0`"
lss.UMGYDE.preset.degree0.result$tuned.result |>
  data.plot(plt.title,
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = "spans", 
              ylabel = "RMSE")
rm(plt.title)
```



##### UMGYDE Model Fine-tuning (`degree = 0`)
\

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 0`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1893) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1893) script on _GitHub_.
:::

Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
```{r, eval=FALSE}
lss.fine_tune.loop_starter <- 
  c(lss.UMGYDE.preset.degree0.result$tuned.result$parameter.value[1], 
    lss.UMGYDE.preset.degree0.result$tuned.result$parameter.value[3], 
    8)

cache_file.base_name <- "UMGYDE.degree0.tuning-span"

lss.UMGYDE.fine_tune.degree0.result <- 
  model.tune.param_range(lss.fine_tune.loop_starter,
                         UMGYDE.fine_tune.degree0.data.path,
                         cache_file.base_name,
                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree0)
```
```{r}
lss.fine_tune.loop_starter
str(lss.UMGYDE.fine_tune.degree0.result)
```

Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 0`:
```{r}
plt.title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree` = 0"

lss.UMGYDE.fine_tune.degree0.result$tuned.result |>
  data.plot(plt.title, 
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = "spans", 
              ylabel = "RMSE")
rm(plt.title)
```
Now, we can add the _UMGYDE Model Tuning_ result for `degree = 0` to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.UMGYDE0 <- RMSEs.ResultTibble.UMGYDE |> 
  RMSEs.AddRow("Tuned UMGYDE.d0 Model", 
               lss.UMGYDE.fine_tune.degree0.result.best_RMSE,
               comment = "UMGYDE Model computed using function call: `loess(degree = 0, span = %1)`" |>
                 msg.glue(lss.UMGYDE.fine_tune.degree0.result.best_span))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYDE0)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
:::

#### UMGYDE Model Tuning: Step 2 (`degree = 1`)
\

##### Pre-configuration: `span` Range Determination
\

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration  (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1944) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1944) script on _GitHub_.
:::

Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
```{r, eval=FALSE}
  lss.UMGYDE.preset.degree1.result <- 
    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
```
```{r}
str(lss.UMGYDE.preset.degree1.result)
```

Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
```{r}
lss.UMGYDE.preset.degree1.result$tuned.result |>
  data.plot(title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 1`",
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = "spans", 
              ylabel = "RMSE")
```

##### UMGYDE Model Fine-tuning (`degree = 1`)
\

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 1`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2007) script on _GitHub_.
:::

Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
```{r, eval=FALSE}
lss.fine_tune.loop_starter <- 
  c(lss.UMGYDE.preset.degree1.result$tuned.result$parameter.value[1], 
    lss.UMGYDE.preset.degree1.result$tuned.result$parameter.value[3], 
    8)

cache_file.base_name <- "UMGYDE.degree1.tuning-span"

lss.UMGYDE.fine_tune.degree1.result <- 
  model.tune.param_range(lss.fine_tune.loop_starter,
                         UMGYDE.fine_tune.degree1.data.path,
                         cache_file.base_name,
                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree1)
```
```{r}
lss.fine_tune.loop_starter
str(lss.UMGYDE.fine_tune.degree1.result)
```

Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 1`:
```{r}
lss.UMGYDE.fine_tune.degree1.result$tuned.result |>
  data.plot(title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree = 1`", 
                             xname = "parameter.value", 
                             yname = "RMSE", 
                             xlabel = "spans", 
                             ylabel = "RMSE")
```

Now, we can add the _UMGYDE Model Tuning_ result for `degree = 1` to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.UMGYDE1 <- RMSEs.ResultTibble.UMGYDE0 |> 
  RMSEs.AddRow("Tuned UMGYDE.d1 Model", 
               lss.UMGYDE.fine_tune.degree1.result.best_RMSE,
               comment = "UMGYDE Model computed using function call: `loess(degree = 1, span = %1)`" |>
                 msg.glue(lss.UMGYDE.fine_tune.degree1.result.best_span))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYDE1)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
:::

#### UMGYDE Model Tuning: Step 3 (`degree = 2`)
\

##### Pre-configuration: `span` Range Determination
\

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning: Pre-configuration (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2056) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2057) script on _GitHub_.
:::

Below the most significant part of the code performing the current model tuning, the _Pre-configuration Step_ is provided:
```{r, eval=FALSE}
  spans <- seq(0.0005, 1, 0.001)
  lss.UMGYDE.preset.degree2.result <- 
    tune.model_param(spans, train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
```
```{r}
str(lss.UMGYDE.preset.degree2.result)
```

Below is the visual representation of the `span` parameter values range we have figured out in this step of tuning:
```{r}
lss.UMGYDE.preset.degree2.result$tuned.result |>
  data.plot(title = "UMGYDE Model, `loess` function args: range of `span` values for `degree = 2`",
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = "spans", 
              ylabel = "RMSE")
```


##### UMGYDE Model Fine-tuning (`degree = 2`)
\

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Fine-tuning (`degree = 2`)](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2119) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2119) script on _GitHub_.
:::

Below the most significant part of the code performing the current model _Fine-tuning_ is provided:
```{r, eval=FALSE}
lss.fine_tune.loop_starter <- 
  c(lss.UMGYDE.preset.degree2.result$tuned.result$parameter.value[1], 
    lss.UMGYDE.preset.degree2.result$tuned.result$parameter.value[3], 
    8)

cache_file.base_name <- "UMGYDE.degree2.tuning-span"

lss.UMGYDE.fine_tune.degree2.result <- 
  model.tune.param_range(lss.fine_tune.loop_starter,
                         UMGYDE.fine_tune.degree2.data.path,
                         cache_file.base_name,
                         train_UMGY_SmoothedDay_effect.RMSE.cv.degree2)
```
```{r}
lss.fine_tune.loop_starter
str(lss.UMGYDE.fine_tune.degree2.result)
```

Below is the visual representation of the current model _Fine-tuning_ results for the parameter value: `degree = 2`:
```{r}
lss.UMGYDE.fine_tune.degree2.result$tuned.result |>
  data.plot.left_detailed(title = "Fine-tuned UMGYDE Model with `loess` parameter: `degree = 2`", 
                             title.left = "Left Part of the Chart Above (Zoomed in)",
                             left.n = 8,
                             xname = "parameter.value", 
                             yname = "RMSE", 
                             xlabel1 = "spans", 
                             ylabel1 = "RMSE")
```

::: {.noteblock data-latex=""}
The custom data visualization function [data.plot.left_detailed](#func.data.plot.left_detailed) we used above is described in the [Data Helper Functions] section of [Appendix A](#appndx_a).
:::


Now, we can add the _UMGYDE Model Tuning_ result for `degree = 2` to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.UMGYDE2 <- RMSEs.ResultTibble.UMGYDE1 |> 
  RMSEs.AddRow("Tuned UMGYDE.d2 Model", 
               lss.UMGYDE.fine_tune.degree2.result.best_RMSE,
               comment = "UMGYDE Model computed using function call: `loess(degree = 2, span = %1)`" |>
                 msg.glue(lss.UMGYDE.fine_tune.degree2.result.best_span))
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYDE2)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
:::

\newpage

#### UMGYDE Model Tuning: Re-training with the Best `degree` & `span` Parameters
\

::: {.noteblock data-latex=""}
The complete version of the source code provided in this section are available in the [UMGYDE Tuned Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#2169) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2169) script on _GitHub_.
:::

Now, we can calculate the _Regularized UMGYDE Effect_ by retraining our model on the entire `edx` dataset with the best values of the `degree` and `span` parameters we figured out above, for the definitive _Root Mean Squared Error_ calculation and use in subsequent processing.

The most significant part of the code that performs this operation is shown below:
```{r, eval=FALSE}
lss.best_results <- data.frame(degree = degree, 
                         span = c(lss.UMGYDE.fine_tune.degree0.result.best_span,
                                  lss.UMGYDE.fine_tune.degree1.result.best_span,
                                  lss.UMGYDE.fine_tune.degree2.result.best_span),
                         
                         RMSE = c(lss.UMGYDE.fine_tune.degree0.result.best_RMSE, 
                                  lss.UMGYDE.fine_tune.degree1.result.best_RMSE,
                                  lss.UMGYDE.fine_tune.degree2.result.best_RMSE))

lss.best_RMSE.idx <- which.min(lss.best_results$RMSE)


lss.UMGYDE.best_params <- 
  c(degree =  lss.best_results[lss.best_RMSE.idx, "degree"],  # 1
    span = lss.best_results[lss.best_RMSE.idx, "span"], # 0.00087,
    RMSE = lss.best_results[lss.best_RMSE.idx, "RMSE"]) # 0.8568619

lss.best_degree <- lss.UMGYDE.best_params["degree"]
lss.best_span <- lss.UMGYDE.best_params["span"]
lss.best_RMSE <- lss.UMGYDE.best_params["RMSE"]

put_log2("Re-training model using `loess` function with the best parameters: 
span = %1, degree = %2", lss.best_span, lss.best_degree)

lss.UMGYD_effect <- edx |> 
  train_UMGY_SmoothedDay_effect(lss.best_degree, lss.best_span)
```
```{r}
lss.UMGYDE.best_params
str(lss.UMGYD_effect)
```


::: {.noteblock data-latex=""}
Here we use the helper function [train_UMGY_SmoothedDay_effect](#func.train_UMGY_SmoothedDay_effect) described above in the [UMGYDE Model: Helper Functions] section.
:::

Let's now visualize final Smoothed Day effect we have obtained:
```{r}
lss.UMGYD_effect |>
  ggplot(aes(x = days)) +
  geom_point(aes(y = de), size = 3, alpha = .5, color = "grey") + 
  geom_line(aes(y = de_smoothed), color = "red")
```

::: {.noteblock data-latex=""}
It should be noted, however, that the graph above is not as smooth as before, although the data now provides better results.
:::


We calculate the _Root Mean Squared Error_ for the ultimately computed _UMGYDE Effect_ using the helper function [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above in the [UMGYDE Model: Helper Functions] section above as follows:
```{r, eval=FALSE}
lss.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(lss.UMGYD_effect)
```

Finally, we add the definitive result for the current model to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.UMGYDE.tuned <- RMSEs.ResultTibble.UMGYDE2 |> 
  RMSEs.AddRow("Tuned UMGYDE Best Model", 
               lss.UMGYD_effect.RMSE,
               comment = "UMGYDE Model computed using `loess` function call with the best degree & span values.")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYDE.tuned)
```

::: {.noteblock data-latex=""}
Here use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A](#appndx_a).
:::

Finally, let's regularize our tuned model as we did with the previous ones.

\newpage

### UMGYDE Model Regularization
\

#### UMGYDE Model Regularization: Mathematical Description
\

We have already explained the idea of _Linear Model Regularization_ in the [UME Model Regularization] section above. We have also seen how the formula \@ref(eq:ME-penalty) for adding a penalty to the _UME Model_ is transformed into the formula \@ref(eq:GE-penalty) for the _UMGE Model_ and then into the formula \@ref(eq:GYE-penalty) for the _UMGYDE Model_. For the current model, this formula takes the form:

\begin{equation}
\sum_{i,j} \left(y_{u,i} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j}) - s(d_{i,j})\right)^2 + \lambda \sum_{i,j} s(d_{i,j})^2
(\#eq:DE-penalty)
\end{equation}

And the formula \@ref(eq:ME-regularized) for calculating the values of the _treatment effect_ that minimizes the equation will take the form:

\begin{equation}
\hat{s}(d_{i,j}, \lambda) = \frac{1}{\lambda + n_d} \sum_{r=1}^{n_{d}} \left(Y_{i,j} - \mu - \alpha_i - \beta_j - g_{i,j} - \gamma(v_{i,j})\right)
(\#eq:DE-regularized)
\end{equation}

where $n_d$ is the number of ratings made on the day $d$. 

As with the previous models, we implement the _Regularization_ method for the current model in the following three steps:

  1. **Pre-configuration:** Preliminary determination of the optimal range of $\lambda$ values for the *K-Fold Cross Validation* samples (in *this Project* we use $K = 5$);
  
  2. **Fine-tuning:** figuring out the value of $\lambda$ that minimizes the model's RMSE.
  
  3. **Retraining:** retraining the model with the best value of the parameter $\lambda$ obtained in the previous step.

\newpage

#### UMGYDE Model Regularization: Pre-configuration
\

::: {.noteblock data-latex=""}
The complete version of the source code shown in this section is available in the [UMGYDE Model Regularization: Pre-configuration](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2322) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2322) script on _GitHub_.
:::

Let's perform the preconfiguration to determine the appropriate range of $\lambda$ for subsequent fine-tuning of our current model:

We are going to use the [tune.model_param](#func.tune.model_param) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a), passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) parameter.

Below we provide the most significant part of the code that performs this operation:
```{r, eval=FALSE}
  lambdas <- seq(0, 256, 16)
  cv.UMGYDE.preset.result <- 
    tune.model_param(lambdas, regularize.test_lambda.UMGYD_effect.cv)
```
```{r}
str(cv.UMGYDE.preset.result)
cv.UMGYDE.preset.result$best_result
```

Now, let's visualize the results of the $\lambda$ range preconfiguration:
``` {r}
cv.UMGYDE.preset.result$tuned.result |>
  data.plot(title = TeX(r'[UMGYDE Model Regularization: $\lambda$ Range Pre-configuration]'),
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = TeX(r'[$\lambda$]'), 
              ylabel = "RMSE")
```

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a), which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
:::

\newpage

#### UMGYDE Model Regularization: Fine-tuning
\

::: {.noteblock data-latex=""}
The complete version of the source code shown in this section can be found in the [UMGYDE Model Regularization: Fine-tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2378) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2378) script on _GitHub_.
:::

We are now ready to perform the fine-tuning step of our model _regularization_ process to determine the best value for the $\lambda$ parameter.

Here we are going to use the [model.tune.param_range](#func.model.tune.param_range) function described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a), passing the [regularize.test_lambda.UMGYD_effect.cv](#func.regularize.test_lambda.UMGYD_effect.cv) function as the value of the [fn_tune.test.param_value](#func.model.tune.param_range.args.fn_tune.test.param_value) parameter.

Below we provide the most significant part of the code that performs this operation:
```{r, eval=FALSE}
endpoints <- 
  get_fine_tune.param.endpoints(cv.UMGYDE.preset.result$tuned.result)

UMGYDE.loop_starter <- c(endpoints["start"], 
                        endpoints["end"], 
                        8)

cache.base_name <- "UMGYDE.rglr.fine-tuning"

UMGYDE.rglr.fine_tune.results <- 
  model.tune.param_range(UMGYDE.loop_starter,
                         UMGYDE.rglr.fine_tune.cache.path,
                         cache.base_name,
                         regularize.test_lambda.UMGYD_effect.cv)
```
```{r}
str(UMGYDE.rglr.fine_tune.results)
UMGYDE.rglr.fine_tune.results$best_result
```

::: {.noteblock data-latex=""}
Under the hood, this code block internally calls the helper function [get_fine_tune.param.endpoints](#func.get_fine_tune.param.endpoints) described in the [Regularization: Common Helper Functions](#appndx_a.rglr.common_helper.functions) section of [Appendix A](#appndx_a) to figure out the boundaries of the range of values from the nearest neighborhood of the value corresponding to the best `RMSE` in the data passed in as a parameter.
:::

\newpage

Let's visualize the fine-tuning results:
```{r}
UMGYDE.rglr.fine_tune.results$tuned.result |>
  data.plot(title = "UMGYDE Model Regularization: Fine-tuned result",
              xname = "parameter.value",
              yname = "RMSE",
              xlabel = TeX(r'[$\lambda$]'),
              ylabel = str_glue("Deviation from the best RMSE value (",
                                as.character(round(UMGYDE.rglr.fine_tune.RMSE.best, digits = 7)),
                                ")"),
              normalize = TRUE)
```

::: {.noteblock data-latex=""}
We use the custom data visualization function [data.plot](#func.data.plot) described in the [Data Helper Functions](#appndx_a.data_helper.functions) section of [Appendix A](#appndx_a), which is defined in the [Data Visualization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L447) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L592) script on _GitHub_.
:::

\newpage

#### UMGYDE Model Regularization: Retraining Model with the best $\lambda$
\

::: {.noteblock data-latex=""}
The complete version of the source code shown in this section is available in the [UMGYDE Regularized Model: Retraining with the best params](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2417) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2417) script on _GitHub_.
:::

Now, we can compute the _Regularized UMGYDE Effect_ by re-training our model on the entire `edx` dataset with the best value of the $\lambda$ parameter we have just figured out and use it in subsequent analysis.

The most significant part of the code for this operation is shown below: 
```{r, eval=FALSE}
  best_result <- UMGYDE.rglr.fine_tune.results$best_result
  UMGYDE.rglr.best_lambda <- best_result["param.best_value"]
  UMGYDE.rglr.best_RMSE <- best_result["best_RMSE"]
  
  put_log1("Re-training Regularized User+Movie+Genre+Year+(Smoothed)Day Effect Model for the best `lambda`: %1...",
           UMGYDE.rglr.best_lambda)
  
  rglr.UMGYD_effect <- edx |> 
    regularize.train_UMGYD_effect(UMGYDE.rglr.best_lambda)
```
```{r}
  str(rglr.UMGYD_effect)
```


::: {.noteblock data-latex=""}
Here we use the helper function [regularize.train_UMGYD_effect](#func.regularize.train_UMGYD_effect) described above in the [UMGYDE Model: Helper Functions] section.
:::

We calculate the _Root Mean Squared Error_ for the ultimately computed _Regularized UMGYDE Effect_ using the helper function [calc_UMGY_SmoothedDay_effect.RMSE.cv](#func.calc_UMGY_SmoothedDay_effect.RMSE.cv) described above in the [UMGYDE Model: Helper Functions] section as follows:
```{r, eval=FALSE}
  rglr.UMGYD_effect.RMSE <- calc_UMGY_SmoothedDay_effect.RMSE.cv(rglr.UMGYD_effect)
```

As always, we add the definitive result for the current model to our _Result Table_:
```{r, eval=FALSE}
RMSEs.ResultTibble.UMGYDE.rglr.tuned <- RMSEs.ResultTibble.UMGYDE.tuned |> 
  RMSEs.AddRow("Regularized UMGYDE Model", 
               rglr.UMGYD_effect.RMSE,
               comment = "The best tuned and regularized UMGYDE Model.")
```
```{r}
RMSE_kable(RMSEs.ResultTibble.UMGYDE.rglr.tuned)
```

::: {.noteblock data-latex=""}
Now, we have a better result than the ones for the previous models, but still insufficient to meet the Project Objective. Let's see what else we can do to achieve our ultimate goal. 
:::

\newpage

#### UMGYDE Model: Final Holdout Test (Preliminary Assessment)
\

::: {.noteblock data-latex=""}
The complete version of the source code shown in this section is available in the [UMGYDE Model: Final Holdout Test](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2498) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L2498) script on _GitHub_.
:::

Let's see what we have achieved so far, using the `final_holdout_test` dataset for the first time.
Firstly, we compute predictions for our current model:
```{r, eval=FALSE}
final.UMGYDE.predicted <- final_holdout_test |>
  UMGY_SmoothedDay_effect.predict(rglr.UMGYD_effect)
```
```{r}
str(final.UMGYDE.predicted)
```
::: {.noteblock data-latex=""}
Here we use the helper function [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) described above in the [UMGYDE Model: Helper Functions] section.
:::

Then we compute the _RMSE_ and add the result to our _Result Table_:
```{r, eval=FALSE}
final.UMGYDE.predicted.RMSE <- rmse2(final_holdout_test$rating,
                                     final.UMGYDE.predicted$predicted)

final.RMSEs.ResultTibble.UMGYDE.rglr.tuned <- RMSEs.ResultTibble.UMGYDE.rglr.tuned |> 
  RMSEs.AddRow("Best UMGYDE Model (Final Test)", 
               final.UMGYDE.predicted.RMSE,
               comment = "Final Holdout Test of the best tuned and regularized UMGYDE Model.")
```

::: {.noteblock data-latex=""}
Here we use the helper function [rmse2](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) to calculate the _RMSE_ that is defined in the  [(R)MSE-related functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L18) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L28) script on _GitHub_.
:::

And finally, we print out the results:
```{r}
RMSE_kable(final.RMSEs.ResultTibble.UMGYDE.rglr.tuned)
```

::: {.noteblock data-latex=""}
As expected, we have not yet achieved a result that meets our Project Objective.
:::

As explained in the [Chapter 24 `Matrix Factorization`](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/matrix-factorization.html) of the _Course Textbook_, so far our models _"ignore an important source of information related to the fact that groups of movies have similar rating patterns and groups of users have similar rating patterns as well..."_ [@IDS2_24]

Then the author shows that in this case, the _Matrix Factorization_ method can considerably improve our results. In the next section, we will apply this method to our current model and see what we get.

\newpage


