# Conclusion
\

In this project, a _Machine Learning Algorithm_ was successfully developed for a _Recommender System_ (hereafter referred to as _RS MLA_) to predict movie ratings using the [10M version of the MovieLens](http://grouplens.org/datasets/movielens/10m/) dataset. 

Since it was needed to convert the original dataset into a _Data Source_, suitable for processing by the _RS MLA_, a package [edx.capstone.movielens.data], specifically designed for this purpose, was developed and used, providing the _RS MLA_ with the necessary datasets.

Following the Netflix Grand Prize Contest requirements, the _Root Mean Squared Error (RMSE)_ metric was used to evaluate the accuracy of our models.


By incorporating essential factors such as overall average rating, movie, user, and some other observable effects, as well as efficient techniques such as _Regularization_ and _Matrix Factorization_ methods, the accuracy was significantly improved compared to the baseline model.

The baseline model was the _Overall Mean Rating_ model described in the [Overall Mean Rating (OMR) Model] section.

The following effects were taken into account:

  - ***User:*** based on which the _User Effect (UE) Model_ described in the [User Effect (UE) Model] section was built (significantly improved the _RMSE_ compared to the baseline model);
  - ***Movie:*** based on which (and the _User Effect_) the _Regularized User+Movie Effect (UME) Model_ described in the [User+Movie Effect (UME) Model] section was eventually built (even better improved the _RMSE_ compared to the previous (*UE*) model);
  - ***Genre:*** based on which (and the previous effects) the _Regularized User+Movie+Genre Effect (UMGE) Model_ described in the [User+Movie+Genre Effect (UMGE) Model] section was built (even after _regularization_ it showed very little improvement in _RMSE_ compared to the previous (*UME*) model; before regularization, for some reason, there was no improvement at all);
  - ***Year:*** based on which (and the previous effects) the _Regularized User+Movie+Genre+Year Effect (UMGYE) Model_ described in the [User+Movie+Genre+Year Effect (UMGYE) Model] section was built (provided a much better improvement in _RMSE_ compared to the previous (*UMGE*) model but still two orders of magnitude less than the *UE* and *UME* models showed);
  - ***Day*** based on which (and the previous effects) the _Regularized (and Tuned) User+Movie+Genre+Year+Day Effect (UMGYDE) Model_ described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section was built (showed almost twice better improvement than the previous (*UMGYE*) model but still not good enough to meet the *Project Objective*);.
  - ***Day (Matrix Factorization):*** (described in the [UMGYDE Model: Matrix Factorization (MF)] section) *Matrix Factorization* method performed on the _Regularized UMGYDE Model_ provided substantial improvement comparable to that shown by the *UE* and *UME* models, and finally permitted to reach the *Project Objective*. 

The *Result Summary Table* constructed below shows in detail the progress of our *Recommender System* improvement:

```{r, eval=FALSE}
total.RMSEs.ResultTibble <- RMSEs.AddDiffColumn(final.MF.RMSEs.ResultTibble)
```
```{r}
RMSE.Total_kable(total.RMSEs.ResultTibble)
```


\newpage

