```{r setup, include=FALSE, echo = FALSE}
```

---
title: "Capstone Movielens Report"
site: bookdown::bookdown_site
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
envir:
  parent.frame()
output: 
  bookdown::pdf_document2: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{awesomebox}
    - \usepackage{hyperref}
    - \usepackage[natbib=true, 
                  style=numeric, 
                  backref=true, 
                  sorting=none]{biblatex}
    - \hypersetup{backref,
          pdfpagemode=Normal,
          colorlinks=true,
          implicit=false}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

\newenvironment{infobox}[1]
  {
  \begin{itemize}
  \renewcommand{\labelitemi}{
    \raisebox{-.7\height}[0pt][0pt]{
      {\setkeys{Gin}{width=3em,keepaspectratio}
        \includegraphics{images/#1}}
    }
  }
  \setlength{\fboxsep}{1em}
  \begin{blackbox}
  \item
  }
  {
  \end{blackbox}
  \end{itemize}
  }

```{r child = '01.intro.Rmd'}
```

```{r child = '02-0.methods.Rmd'}
```

```{r child = '02-3.OMR-model.Rmd'}
```

```{r child = '02.4.UE-model.Rmd'}
```

```{r child = '02.5.UME-model.Rmd'}
```

```{r child = '02.6.UMGE-model.Rmd'}
```

```{r child = '02.7.UMGYE-model.Rmd'}
```

```{r child = '02.8-0.UMGYDE-model.Rmd'}
```

```{r child = '02.8-1.MF.UMGYDE-model.Rmd'}
```
```{r child = '03.conclusion.Rmd'}
```

```{r child = '04.appendix.Rmd'}
```


